Study protocol

### 2021-12-23 Manuscript/S1.Protocol.Rmd
some proof reading

Now the annotation file is ready for the manual classification records.
The annotation file has a column called `Rev_manual`, where records need to be classified as "positive" (y) or "negative" (n) matches by the user.
We suggest manually labelling an **initial training set** of 250 records, which should be sufficient if a minimum ~20% positivity rate is present (see the section about model hyperparameter optimisation)./
The function `plot_classification_trends()` can help visualise the trend of the positives/negatives as the number of classified records increases./

@@

- A results summary page reporting the number of records in need of manual review (which includes "unk", "check", and unreviewed "y" records), the changes, and the final distribution of the labels.
It also shows other information like the number of features in the DTM, the path to the parent file from which the annotation file was created, the replication number (see later). The content of this summary is also saved as a CSV file in the Results folder.
- A variable importance page which list the used terms in order of the fraction of BART trees in which they were used. If an ensemble of models is used, a more robust score is computed, taking the ratio of the mean of the term tree fraction among models and its standard deviation.
- The arguments passed to the function if different from the default, useful for reproducibility.
- A classification performance summary. The procedure may take some time and requires `cmdstan` installed on the machine. Therefore the `compute_performance` argument is set to `FALSE` by default.

@@

It is not uncommon for the first query used in a systematic review not to be the most effective one, especially in terms of sensitivity.
We tried to address the problem by creating an automatic query generation system.\
The solution is experimental and greatly favours sensitivity at the expense of specificity.
This is the general query generation mechanism:

@@

# The last annotation file and posterior sample matrix in the session are found;
# the most predictive terms (based on the importance score) are chosen and
# simple prediction trees are used to map the terms to a random subset of the
# posterior probabilities (extracted from the posterior sample matrix saved
# during the last CR iteration). The score threshold and the number of trees can
# be chosen by the user; less stringent values can greatly increase computation
# time. By default results will be saved in file called rule_data.rds in the
# session folder.

@@

# The 'candidate_queries' contains the rules and the DMT and the labels on which
# the rules were built, which need to be passed to
# generate_rule_selection_set(). This function selects the most effective
# (higher positive/negative matches delta) rules; also adds negative terms to
# increase specificity. A data frame is generated (or automatically saved if
# save_path is set). The output proposes groups of equivalent (in terms of the
# number of positive matches found) groups of query, ordered by specificity; for
# each group, the user needs to select the best rule by setting the
# selected_rule column to TRUE. The groups are in order of growing
# sensitivity/decreasing specificity, so it may make sense to exclude the last
# groups totally in order to avoid too many search results.

@@

# Once the manual selection is performed the selected rules can be further
# simplified in order to remove redundant rules and terms. The aim is to provide
# the shortest rule without loss of retrieving accuracy.

@@

Once the new query was generated, a second search session called `Session2` was created, using the strategy described in the protocol.
Due to the lower specificity of the second query, particular care may be needed in managing the far larger amount of records:
multiple record files may need to be downloaded from Pubmed, EMBASE, and SCOPUS since they have limits on the number of records one can download at once;
also, the machine learning classification processing time increases proportionally with the number of records to label.\
It is advisable then to consider removing the less specific rules iteratively from the new query until a manageable number of records is obtained, considering that the probability of finding new positive matches not already found by more specific queries drops exponentially.\

Once the new records are collected, `enrich_annotation_file('Session2')` (or any other new session name) can be used to perform the new CR iterations.
It may be possible that during the first CR iteration, the number of records requiring manual review is a significant number:
we suggest evaluating still not more than 250, keeping in mind to set the `stop_on_unreviewed` argument to `FALSE`.

@@

A number of tools are available to evaluate the classification performance.\
As said before, a result file is stored in the session folder for each CR iteration with information on the classification status;
remember to run `consolidate_results(session_name)` if you want these results to take into account the manual review of the predicted labels.\
`compute_changes()` is a simple function that take an annotation data frame and computes the changes from the last annotation iteration.\
The primary function for result analysis is `estimate_performance()`.
The function uses a Bayesian model to estimate how the probability of a positive match drops as records' lower boundary of the posterior predictive interval decreases.
This model computes the cumulative distribution of possibly missed positive records, which permits extraction of the engine's theoretical sensitivity and efficiency to lower 90% credibility boundaries (i.e., the indicators are better than these values with 95% probability).
These boundaries depict worse case scenarios since it is impossible to know the actual number of missed positive records.\
The function returns the Bayesian $R^2$ of the model (values below 85-90% would invalidate the model analysis), the posterior sensitivity, the observed and theoretical number positives, the expected efficiency given the theoretical number of positives (that is 1 - the number of reviewed records above the number of records to review to find the predicted number of positives according to a negative hypergeometrical distribution).
Also, the function plots the cumulative distribution of the observed and theoretical number of positive records.\
`extract_var_imp()` extract the most relevant terms used by the BART model and summarises their relevancy for the machine learning model and their statistical relevancy in a simple generalised linear model. A discrepancy between these two scores indicates a non-linear effect/interaction between terms.

@@

We utilise a “grid search” algorithm to find the best set of hyperparameters.
We tested these tools on our dataset, manually labelling the first 1200 records, ordered by simple query match.\
The first step is to create a folder where to store the file required for the search, for example, *Grid Search*.
Then a fully reviewed record file in the format generated by `create_annotation_file()` is necessary;
this file can be put in the *Grid Search*, but it is not mandatory.\

@@

with `records` being the fully annotated data frame or a file path to it.
`prev_classification` can be used to import a different classification file with prelabeled records.

@@

Once the grid search is performed, the function `analyse_grid_search()` can be used to analyse its results.
This function uses a partition tree analysis to identify hyperparameter sets (**performance clusters**) with different mean performance scores.
As said before, the default score is Sensitivity x Efficiency;
alternatives are the Positive Rate (i.e., positive records found over total records) or Positive Rate x Sensitivity.\
The function produces a data frame with the score and the cluster of reference of each combination of parameters, the best hyperparameter set (i.e., the most efficient set among the most sensitive in the best cluster) and the best set for each cluster.
Also, the function creates a plot to visualise the individual impact on performance of each hyperparameter.

>>>>

Now the annotation file is ready for the manual classification of records.
The annotation file has a column called `Rev_manual`, where records need to be classified as "positive" (y) or "negative" (n) matches by the user.
We suggest manually labelling an **initial training set** of 250 records, which should be sufficient if a minimum ~20% positivity rate is present (see the section about model hyperparameter optimisation)./
The function `plot_classification_trends()` can help visualise the trend of the positives/negatives as the number of classified records increases./

@@

- A results summary page reporting the number of records in need of manual review (which includes "unk", "check", and unreviewed "y" records), the changes, and the final distribution of the labels.
It also shows other information like the number of features in the DTM, the path to the parent file from which the annotation file was created, the replication number (see later). The content of this summary is also saved as a CSV file in the Results folder.
- A variable importance page that lists the used terms in order of the fraction of BART trees in which they were used. If an ensemble of models is used, a more robust score is computed, taking the ratio of the mean of the term tree fraction among models and its standard deviation.
- The arguments passed to the function if different from the default, useful for reproducibility.
- A classification performance summary. The procedure may take some time and requires `cmdstan` installed on the machine. Therefore the `compute_performance` argument is set to `FALSE` by default.

@@

It is not uncommon for the first query used in a systematic review not to be the most effective one, especially in terms of sensitivity.
We tried to address the problem by creating an automatic query generation system.\
The solution is experimental and greatly favours sensitivity at the expense of specificity.
The general query generation mechanism is the following:

@@

# The last annotation file and posterior sample matrix in the session are found;
# the most predictive terms (based on the importance score) are chosen and
# simple prediction trees are used to map the terms to a random subset of the
# posterior probabilities (extracted from the posterior sample matrix saved
# during the last CR iteration). The score threshold and the number of trees can
# be chosen by the user; less stringent values can significantly increase
# computation time. By default results will be saved in a file called
# rule_data.rds in the session folder.

@@

# The 'candidate_queries' contains the rules, the DMT and the labels on which
# the rules were built, which must be passed to generate_rule_selection_set().
# This function selects the most effective (higher positive/negative matches
# delta) rules; also adds negative terms to increase specificity. A data frame
# is generated (or automatically saved if save_path is set). The output proposes
# groups of equivalent (in terms of the number of positive matches found) groups
# of query, ordered by specificity; for each group, the user needs to select the
# best rule by setting the selected_rule column to TRUE. The groups are in order
# of growing sensitivity/decreasing specificity, so it may make sense to exclude
# the last groups totally in order to avoid too many search results.

@@

# Once the manual selection is performed the selected rules can be further
# simplified in order to remove redundant rules and terms. The aim is to provide
# the shortest rule without loss of sensitivity.

@@

Once the new query was generated, a second search session called `Session2` was created, using the strategy described in the protocol.
Due to the lower specificity of the second query, particular care may be needed in managing the far larger amount of records:
multiple record files may need to be downloaded from Pubmed, EMBASE, and SCOPUS since they have limits on the number of records one can download at once;
also, the machine learning classification processing time increases proportionally with the number of records to label.\
It is advisable to consider removing the less specific rules iteratively from the new query until a manageable number of records is obtained, considering that the probability of finding new positive matches not already found by more specific queries drops exponentially.\

Once the new records are collected, `enrich_annotation_file('Session2')` (or any other new session name) can be used to perform the new CR iterations.
It may be possible that during the first CR iteration, the number of records requiring manual review is significant:
we suggest evaluating still not more than 250, keeping in mind to set the `stop_on_unreviewed` argument to `FALSE`.

@@

Several tools are available to evaluate the classification performance.\
As said before, a result file is stored in the session folder for each CR iteration with information on the classification status;
remember to run `consolidate_results(session_name)` if you want these results to account for the manual review of the predicted labels.\
`compute_changes()` is a simple function that take an annotation data frame and computes the changes from the last annotation iteration.\
The primary function for result analysis is `estimate_performance()`.
The function uses a Bayesian model to estimate how the probability of a positive match drops as records' lower boundary of the posterior predictive interval decreases.
This model computes the cumulative distribution of possibly missed positive records, which permits extraction of the engine's theoretical sensitivity and efficiency to lower 90% credibility boundaries (i.e., the indicators are better than these values with 95% probability).
These boundaries depict worse case scenarios since it is impossible to know the actual number of missed positive records.\
The function returns the Bayesian $R^2$ of the model (values below 85-90% would invalidate the model analysis), the posterior sensitivity, the observed and theoretical number positives, the expected efficiency given the theoretical number of positives (that is 1 - the number of reviewed records above the number of records to review to find the predicted number of positives according to a negative hypergeometrical distribution).
Also, the function plots the cumulative distribution of the observed and theoretical number of positive records.\
`extract_var_imp()` extract the most relevant terms used by the BART model and summarises their relevancy for the machine learning model and their statistical relevancy in a simple generalised linear model. A discrepancy between these two scores indicates a non-linear effect/interaction between terms.

@@

We utilise a “grid search” algorithm to find the best set of hyperparameters.
We tested these tools on our dataset, manually labelling the first 1200 records, ordered by simple query match.\
The first step is to create a folder to store the file required for the search, for example, *Grid Search*.
Then a fully reviewed record file in the format generated by `create_annotation_file()` is necessary;
this file can be put in the *Grid Search*, but it is not mandatory.\

@@

with `records` being the fully annotated data frame or a file path.
`prev_classification` can be used to import a different classification file with prelabeled records.

@@

Once the grid search is performed, the function `analyse_grid_search()` can be used to analyse its results.
This function uses a partition tree analysis to identify hyperparameter sets (**performance clusters**) with different mean performance scores.
As said before, the default score is Sensitivity x Efficiency;
alternatives are the Positive Rate (i.e., positive records found over total records) or Positive Rate x Sensitivity.\
The function produces a data frame with the score and the cluster of reference of each combination of parameters, the best hyperparameter set (i.e., the most efficient set among the most sensitive in the best cluster) and the best set for each cluster.
Also, the function creates a plot to visualise each hyperparameter's impact on performance.
